Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling\\ \notebyalbert{\small Corregí filiación UNTREF, agregué segunda filiación para Fede (creo que no es preciso poner CBC, Fede?). Diego, ORCID IDs faltantes sacalos de {\tt orcid.org}}

### 2019-12-14 lloveras_2020.tex
Edited by Albert 13/Dec/2019 - 23:28 hs.

As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down loops in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. The amount of down loops in the equatorial latitudes. A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In blue the type 1 lines, populating all the streamer but mostly the mid latitudes. In red the type 2 lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type 3 lines, populating the coronal holes.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of \albert{loops of type 0 (cyan), I (blue), II (red) and III (green)} at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel). See Section \ref{trace} for a definition of the different types of \albert{loops}. \notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors. I suggest these changes: cyan$\rightarrow$blue, blue$\rightarrow$red, red$\rightarrow$violet. In this way, blue will be DOWN loops and red will be UP loops, as in previous papers. The same change applies to Figure 4. Also, how about making Figures 3 and 4 a single Figure of four panels? Just an idea.}}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{\albert{Statistical distribution of DEMT results traced along the type of loops 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} \notebyalbert{The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for a clear reading.}}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blu, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to left the type 0, 1 and 2 field of lines defined in Section \ref{trace}. \notebyalbert{Utilizar los colores del paper de Cecilia, notar que el conductivo debe ser el verde y el energy input flux (h) debe ser el rojo. De paso, haría el verde un poco menos chillón, como en el paper de Ceci, se verá mejor. En el XYOUTS podés poner la letra griega $\phi$,  y para que te salga r,c,h como subíndice pero no pequeño usá: ``!Dp!N", donde p=r,c,h.}}
\label{energia_demt}
\end{center}
\end{figure}

@@

\temp{Parrafo introductorio?}

As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $\Ne$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025, 1.065$ and $1.105\,\mrsun$. The black curve denotes the open-close boundary.

@@

\begin{figure}[h!]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
\caption{Same as Figure \ref{rpoint_demt}, using the density and temperature of AWSoM model to classify legs in type 1, 2 and 3.}
\label{rpoint_awsom}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. The left (right) panels correspond to CR-2082 (CR2208). The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary.}
\label{perf_lat}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
\caption{Average fits of $\Ne(r)$ and $T_e(r)$ for legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions for CR-2082 between DEMT (blue) and AWSoM (red). From left to right: the coronal base electron density $\Ne(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average $\aTm$ along the four types of legs considered in Section \ref{trace}. In each panel the median ($m$) is indicated.}
\label{histos_2082}
\end{center}
\end{figure}

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
CR-2082\\
1  & 0&84 &(\Mi&14&4\%)  &   8&3 &(\Mi&~2&5\%) &   1&30 &(\Mi&10&8\%) \\
2  & 0&74 &(\Mi&21&9\%)  &   8&9 &(\Pl&~1&0\%) &   1&33 &(\Mi&~4&5\%) \\
3  & 0&82 &(\Mi&17&9\%)  &   7&7 &(\Mi&~8&9\%) &   0&98 &(\Mi&~9&5\%) \\
\hline          
CR-2208\\
1  & 0&74 &(\Pl&~6&4\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&12&3\%) \\
2  & 0&62 &(\Pl&~8&2\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
3  & 0&42 &(\Mi&~4&8\%)  &   8&6 &(\Mi&~8&4\%) &   1&04 &(\Mi&~9&7\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. FDEMT values are expressed in absolute terms, while for AWSoM they are informed as a percentual variation relative to the DEMT value.}
\label{tabla_comp}
\end{table}

@@

Figure \ref{perf_lon_vr} show the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open. The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.\\
\diego{can we say something without having traced the lines?}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{Longitude-averaged of radial wind speed at $6\,\mrsun$ given by AWSoM for both rotations.}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

>>>>

\albert{En las discusiones usás type 1, 2 y 3, pero son I, II y III.} As a way of knowing the physical position of the types of lines defined in Section \ref{trace}, the Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of the selected lines at $1.105\,\mrsun$ for both rotations. In cyan the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down loops). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down loops in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. The amount of down loops in the equatorial latitudes. A decrease in the amount of down loops in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In blue the type 1 lines, populating all the streamer but mostly the mid latitudes. In red the type 2 lines, are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type 3 lines, populating the coronal holes.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of \albert{loops of type 0 (cyan), I (blue), II (red) and III (green)} at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel). See Section \ref{trace} for a definition of the different types of \albert{loops}. \notebyalbert{(by ALBERT) The population of DOWN loops in CR-2008 is negligible. These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it.}  \notebyalbert{(by ALBERT) This Figure is great, but I do not quite like the choice of colors. I suggest these changes: cyan$\rightarrow$blue, blue$\rightarrow$red, red$\rightarrow$violet. In this way, blue will be DOWN loops and red will be UP loops, as in previous papers. The same change applies to Figure 4. Also, how about making Figures 3 and 4 a single Figure of four panels? Just an idea.} }
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{\albert{Statistical distribution of DEMT results traced along loops of type 0, I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the coronal base $\NCB\equiv\sqravgN(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. Results for target rotations CR2082 and CR2208 are shown in blue and red color, respectively. In each panel the median value $m$ is indicated.} \notebyalbert{The histogram Figures in this draft need to be improved, in particular font size-and-type need to be optimized for clear reading. Also, we need to improve their X/Y ratio, here I stretched the Y size a bit in the LaTeX source.}}
\label{histos_fulldemt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blu, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to left the type 0, 1 and 2 field of lines defined in Section \ref{trace}. \notebyalbert{The type-0 population in CR-22208 is negligible. These are VERY SMALL loops, I am pretty sure but you and Ceci shoudl check it. This can explain the non-physical $\phi_h<0$ population.} \notebyalbert{Utilizar los colores del paper de Cecilia, notar que el conductivo debe ser el verde y el energy input flux (h) debe ser el rojo. De paso, haría el verde un poco menos chillón, como en el paper de Ceci, se verá mejor. En el XYOUTS podés poner la letra griega $\phi$,  y para que te salga r,c,h como subíndice pero no pequeño usá: ``!Dp!N", donde p=r,c,h.}}
\label{energia_demt}
\end{center}
\end{figure}

@@

\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$). It will first show the Carrington maps of $N_e$ and $T_e$ at the same three heights we showed the same maps for the DEMT results. Then it will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results. As the two targets are highly axis-symmetric, a first quantitative comparison between AWSoM and DEMT will be shown as longitude-averaged latitudinal profiles of the results of both models at a sample height. To make comparisons in distinct magnetic structures, we will also show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results. For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines. This is a LOT of information from which and we need to pull out a few clear conlcusions.}

As an example of the AWSoM results, Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} shows the latitude-longitude maps for $\Ne$ and $T_e$ modeled for CR-2082 and CR-2208 at $r=1.025$, $1.065$ and $1.105\,\mrsun$. The black curve denotes the open-close boundary.

@@

\begin{figure}[h!]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
\caption{Same as Figure \ref{rpoint_demt}, but using the density and temperature of the AWSoM model to classify \albert{its loops in types I, II and III. The model does not exhibit loops of type 0.}}
\label{rpoint_awsom}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. The left (right) panels correspond to CR-2082 (CR2208). The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary.}
\label{perf_lat}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
\caption{\albert{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (blue), II (red), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,height=0.18\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{\albert{Statistical distribution of DEMT (blue) and AWSoM (red) results traced along loops of type I, II and III (from top to bottom), as defined in Section 2.3. From left to right: electron density at the coronal base $\NCB\equiv \Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and loop-averaged electron temperature $\aTm$. In each panel the median value $m$ is indicated.}}
\label{histos_2082}
\end{center}
\end{figure}

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
CR-2082\\
1  & 0&84 &(\Mi&14&4\%)  &   8&3 &(\Mi&~2&5\%) &   1&30 &(\Mi&10&8\%) \\
2  & 0&74 &(\Mi&21&9\%)  &   8&9 &(\Pl&~1&0\%) &   1&33 &(\Mi&~4&5\%) \\
3  & 0&82 &(\Mi&17&9\%)  &   7&7 &(\Mi&~8&9\%) &   0&98 &(\Mi&~9&5\%) \\
\hline          
CR-2208\\
1  & 0&74 &(\Pl&~6&4\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&12&3\%) \\
2  & 0&62 &(\Pl&~8&2\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
3  & 0&42 &(\Mi&~4&8\%)  &   8&6 &(\Mi&~8&4\%) &   1&04 &(\Mi&~9&7\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

@@

Figure \ref{perf_lon_vr} show the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open. The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve.\\
\diego{can we say something without having traced the lines?} \notebyalbert{(by ALBERT) Todo el punto de la última Figura es precisamente decir algo. La comparación con la Figura 10 muestra una anti-correlación entre la densidad basal de DEMT y la velocidad terminal de AWSoM.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{\albert{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6\,\mrsun$ for CR2082 (left panel) and CR2208 (right panel).}}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

\noindent\notebyalbert{Antes de enviar esto a Michigan se precisa un conjunto de conclusiones compacto y claro. Creo que yo las pondría en tres grupos: a) conclusiones DEMT solas (esto incluye estructura termodinámica, up/down loops, energía), b) comparación AWSoM/DEMT (la clobal, es decir promedio longitudinal, y la que difernecia estructuras magnéticas), c) Wind Speed y Densidad basal.}
